### 2007-01-11 Documentation/part2.tex
JK - Modified discussion of tilt errors

For the parameterization of an energy calibration error, two possibilities
are implemented. The first one (method ``T'') is somewhat simpler, 
whereas the second one (method ``C'')
is more accurate, but it requires a careful choice of parameters. 
The first option (method ``T'') is (JK: IS THAT CORRECT? AND ALSO THE NEXT EQUATION? (THERE HAVE BEEN
SOME CHANGES) [WW])
\begin{equation}
s_i(a,b) \equiv s_i(a)+b\cdot s_i\, E'_i/(E'_\mathrm{max}-E'_\mathrm{min}),
\end{equation}
where $E'_{\mathrm{min}}$ and $E'_{\mathrm{max}}$ correspond to {\tt \$emin}
and {\tt \$emax}, and $E'_i$ is the mean (reconstructed) 
energy of the $i$th bin. It is often refered to as a ``tilt'' of the
spectrum, since it describes a linear distortion 
of the event rate spectrum. Note that this definition of a tilt makes
only sense in combination with a large enough normalization error, since
the tilt may also affect the normalization. 
%
The second option (method ``C'') is closer to an actual energy
calibration error, which means that one should test this option whenever
one suspects a large impact of this systematical error.
It is based upon replacing the events in the $i$th bin by the ones at
the energy $(1+b)\cdot E'_i$. If this target energy does not exactly hit
a (discrete) bin energy $E_k$, linear interpolation is used. We use the following approximation:
\begin{eqnarray}
s_i(a,b)&=& (1+b)\cdot \left[ \left( s_{k+1}(a)-s_k(a) \right)\cdot (\delta-k) +s_k(a) \right] \,,\\
\delta&=&b\cdot(i+t_0+ 1/2)+i\,,\nonumber\\
k&=& \mathrm{div}(\delta,1)\,,\nonumber\\
t_0&=&E'_\mathrm{min}/\Delta E_0\,.\nonumber
\end{eqnarray}
Here $\Delta E_0$ is the bin width ({\tt \$emax}-{\tt \$emin})/{\tt \$bins}
and ``div'' refers to the integer part of the division. Note that the
factor $(1+b)$ in the first equation comes from a renormalization of
the bin width, since also the bin width is altered by the replacement of
the energies. Furthermore, special care has to be payed to the limits
 $k<1$ or $k+1>N_\mathrm{bins}$, since there $s_k$ or $s_{k+1}$ may not have been calculated. By default, it is assumed that $s_k$ is
zero in those cases. However, if the event rates are still large at
the limits, errors will be introduced leading to a wrong
estimate of the impact of the calibration error. In this case,
one should truncate the analysis range by a few bins at the boundaries
and therefore ensure in this way that only those $s_i$ are used whose index
$k$ is within the range $0,\ldots, N_\mathrm{bins}-1$ (\cf, \figu{energies}). 
Thus, it is possible to constrain the analysis energy range 
with each rule to an energy window\index{norm}{Energy!window}:
\index{aedl}{rule@{\tt rule}!energy window@{\tt "@energy\_window}}
\begin{quote}
{\tt 
\tb @energy\_window = 4.0 : 50.0 
}
\end{quote}
The default energy window is given between the minimal and maximal reconstructed energy. To be on the save side, reduce analysis window
compared to the bin range on each side by about three times the
energy calibration error.

>>>>

For the parameterization of an energy calibration error, two possibilities
are implemented. The first one (method ``T'') is somewhat simpler, 
whereas the second one (method ``C'')
is more accurate, but it requires a careful choice of parameters. 
The first option (method ``T'') is\footnote{Note that this behaviour
has slightly changed compared to previous \GLOBES\ releases.}
\begin{equation}
s_i(a,b) \equiv s_i(a)+b\cdot s_i \cdot i / N_\mathrm{bins}.
\end{equation}
It is often refered to as a ``tilt'' of the
spectrum, since it describes a linear distortion 
of the event rate spectrum. Note that this definition of a tilt makes
only sense in combination with a large enough normalization error, since
the tilt may also affect the normalization. 
%
The second option (method ``C'') is closer to an actual energy
calibration error, which means that one should test this option whenever
one suspects a large impact of this systematical error.
It is based upon replacing the events in the $i$th bin (mean reconstructed energy $E'_i$)
by the ones at the energy $(1+b)\cdot E'_i$. If the target energy does not exactly hit
a (discrete) bin energy $E_k$, linear interpolation is used. We use the following approximation:
\begin{eqnarray}
s_i(a,b)&=& (1+b)\cdot \left[ \left( s_{k+1}(a)-s_k(a) \right)\cdot (\delta-k) +s_k(a) \right] \,,\\
\delta&=&b\cdot(i+t_0+ 1/2)+i\,,\nonumber\\
k&=& \mathrm{div}(\delta,1)\,,\nonumber\\
t_0&=&E'_\mathrm{min}/\Delta E_0\,.\nonumber
\end{eqnarray}
Here, $E'_\mathrm{min} = {\tt \$emin}$,  $\Delta E_0$ is the bin width
({\tt \$emax}-{\tt \$emin})/{\tt \$bins},
and ``div'' refers to the integer part of the division. Note that the
factor $(1+b)$ in the first equation comes from a renormalization of
the bin width, since also the bin width is altered by the replacement of
the energies. Furthermore, special care has to be payed to the limits
 $k<1$ or $k+1>N_\mathrm{bins}$, since there $s_k$ or $s_{k+1}$ may not have been calculated. By default, it is assumed that $s_k$ is
zero in those cases. However, if the event rates are still large at
the limits, errors will be introduced leading to a wrong
estimate of the impact of the calibration error. In this case,
one should truncate the analysis range by a few bins at the boundaries
and therefore ensure in this way that only those $s_i$ are used whose index
$k$ is within the range $0,\ldots, N_\mathrm{bins}-1$ (\cf, \figu{energies}). 
Thus, it is possible to constrain the analysis energy range 
with each rule to an energy window\index{norm}{Energy!window}:
\index{aedl}{rule@{\tt rule}!energy window@{\tt "@energy\_window}}
\begin{quote}
{\tt 
\tb @energy\_window = 4.0 : 50.0 
}
\end{quote}
The default energy window is given between the minimal and maximal reconstructed energy. To be on the save side, reduce analysis window
compared to the bin range on each side by about three times the
energy calibration error.
